Convolutional Neural Nets for the MNIST Digit Dataset

### 2014-12-13 tex/paper.tex
Added Discussion section

>>>>

%-------------------------------------------------------------------------
\section{Discussion}

Our two convolutional/pooling layer architecture (trained with 500 images) did not significantly outperform
our one convolutional/pooling layer (also trained with 500 images) on the MNIST dataset. In fact, while both nets
performed similarly after 50 iterations of training (to a difference of 1\%), the deeper architecture took more
training iterations to converge, as can be seen on the left side of \ref{fig:accplot}.
This makes it tempting to conclude that a deep network may not be appropriate for this classification task.

What actually seems to be the core issue is the number of training images. While we were able to train both
networks with 500 images (and our shallower network with 1,000), this still represents slightly less than 2\% of
the provided training data \cite{MNIST}. Due to time constraints, we were unable to train with the entire dataset.
Nevertheless, we were able to achieve good performance (about 94\% on our shallower network) despite the small
training set.

While analyzing the digits that are misclassified by our nets, we noticed that there are a sizable number of
digits that are difficult even for humans to discern (see Figure [?] for examples). Our net also seems to have
significant trouble with discerning the number 8, possibly because it has much in common with multiple other
digits like 6 and 9, especially when squished. We feel that training on deformed versions of input images
(say, squished versions of 8's) would significantly improve our net's performance on these digits.
